Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2024-04-10 LaTeX_paper/paper.tex
Split last section, todo: final check

\section{Conclusions}
This section will conclude the paper,
by answering the two questions posed in \cref{document:objective}:

\begin{itemize}
  \item What is the difference in execution time between
                digital and real-world puzzles?
  \item What are the challenges to use the current state of the art algorithms developed for digital
                puzzles in the real-world, and how can we overcome them?
\end{itemize}
And by making some consideration about possible future works related to this problem.

@@

>>>>

\section{Evaluation}
This section will evaluate the proposed solution by measuring
two key metrics: execution time and accuracy. 
The objective of this section is to answer the first question posed in~\cref{document:objective}:
\begin{itemize}
  \item What is the difference in execution time between
                digital and real-world puzzles?
\end{itemize}

@@

\section{Conclusion}

This sections aim to conclude the paper by answering the second question
posed in ~\cref{document:objective}:

\begin{itemize}
  \item What are the challenges to use the current state of the art algorithms developed for digital
                puzzles in the real-world, and how can we overcome them?
\end{itemize}

Ath the end of the section we will also make some consideration about
possible future works related to this problem.
